Concurrent Programming with CXL

### 2020-06-16 book/paper.tex
Added a chapter outline

\chapter{Introduction to Programming with CXL}

@@

\chapter{The Problem of Concurrent Programming}

@@

\chapter{Critical Sections}

@@

\chapter{Na\"{\i}ve Attempts at Implementing Critical Sections}

@@

\chapter{CXL Methods and Pointers}
\index{CXL method}

@@

\chapter{Spinlock}
\index{spinlock}
\glsadd{spinlock}

@@

\chapter{Locks and the Synch Module}
\index{lock}
\index{synch module}

@@

\chapter{Reader/Writer Locks using Busy Waiting}
\index{reader/writer lock}
\glsadd{reader/writer lock}

@@

\chapter{Reader/Writer Lock, Part 2}

@@

\chapter{Deadlock}
\index{deadlock}
\glsadd{deadlock}

@@

\chapter{Semaphores}
\index{semaphore}
\glsadd{semaphore}

@@

\chapter{Bounded Buffer}
\index{bounded buffer}
\index{producer/consumer problem}
\glsadd{producer/consumer problem}

@@

\chapter{Split Binary Semaphores}
\index{split binary semaphore}

@@

\chapter{Mesa Condition Variables in CXL}

@@

\chapter{Actors and Synchronized Queues}
\index{actor model}
\glsadd{actor model}

@@

\chapter{Non-Blocking Synchronization}
\index{non-blocking synchronization}
\glsadd{non-blocking synchronization}

@@

\chapter{Barrier Synchronization}
\index{barrier synchronization}
\glsadd{barrier synchronization}

@@

\chapter{Networking: Alternating Bit Protocol}
\index{alternating bit protocol}

>>>>

The book proceeds as follows:

\begin{itemize}
\item In Chapter~\ref{ch:cxlintro} introduces the CXL programming
language, as it provides the language for presenting synchronization
problems and solutions.
\item Chapter~\ref{ch:concurrent} introduces the problem of
concurrent programming through a simple example in which two processes
are concurrently incrementing a counter;
\item Chapters~\ref{ch:cxlvalues} and~\ref{ch:cxlmachine} present some more
details of the CXL language and machine to understand the problem
underlying concurrency better.
\item Chapter~\ref{ch:critical} introduces the concept of a critical
section.
\item Chapter~\ref{ch:naive} presents various flawed implementations
of critical sections.
\item Chapter~\ref{ch:peterson} introduces Peterson's Algorithm, an
elegant solution to the mutual exclusion problem.
\item Chapter~\ref{ch:method} gives some more details on the CXL
language.
\item Chapter~\ref{ch:spinlock} introduces hardware-supported locks
for mutual exclusion.  Chapter~\ref{ch:synch} presents a CXL module
that supports locks and other synchronization primitives.
\item Chapters~\ref{ch:rdwrbusy} and~\ref{ch:rdwr2} present the
abstraction and implementation of reader/writer
locks, which allow multiple processes in a critical section if they are
all only executing read-only accesses.
Chapter~\ref{ch:rdwrbusy} also talks about busy-waiting, which is
an undesirable approach to synchronize processes.
\item Chapter~\ref{ch:deadlock} introduces the notion of \emph{deadlock}
where a set of processes are indefinitely waiting for one another to
release a resource.
\item Chapter~\ref{ch:semaphore} introduces a generalization of locks
that is good not only for mutual exclusion but also for waiting for
certain application-level conditions.
\item Chapters~\ref{ch:bb} and~\ref{ch:sbs} introduce the bounded buffer
problem and various solutions.
\item Chapter~\ref{ch:starvation} talks about the problem that in some
synchronization solutions, processes may not be able to get access to a
resource they need, and a solution for the reader/writer problem.
\item Chapters~\ref{ch:monitors} and~\ref{ch:mesa} present monitors and
condition variables, another approach to process synchronication.
\item Chapter~\ref{ch:actor} presents the actor model as an approach to
synchronization.
\item Chapter~\ref{ch:nonblocking} shows solutions to process synchronization
that prevent processes waiting for one another more than a bounded number of
steps.
\item Chapter~\ref{ch:barrier} introduces barrier synchronization, useful in
high-performance computing applications such as parallel simulations.
\item Chapter~\ref{ch:abp} presents a problem and a solution to the distributed
systems problem of having two processes communicate over an unreliable network.
\end{itemize}

\chapter{Introduction to Programming with CXL}
\label{ch:cxlintro}

@@

\chapter{The Problem of Concurrent Programming}
\label{ch:concurrent}

@@

\chapter{Critical Sections}
\label{ch:critical}

@@

\chapter{Na\"{\i}ve Attempts at Implementing Critical Sections}
\label{ch:naive}

@@

\chapter{CXL Methods and Pointers}
\label{ch:method}
\index{CXL method}

@@

\chapter{Spinlock}
\label{ch:spinlock}
\index{spinlock}
\glsadd{spinlock}

@@

\chapter{Locks and the Synch Module}
\label{ch:synch}
\index{lock}
\index{synch module}

@@

\chapter{Reader/Writer Locks using Busy Waiting}
\label{ch:rdwrbusy}
\index{reader/writer lock}
\glsadd{reader/writer lock}

@@

\chapter{Reader/Writer Lock, Part 2}
\label{ch:rdwr2}

@@

\chapter{Deadlock}
\label{ch:deadlock}
\index{deadlock}
\glsadd{deadlock}

@@

\chapter{Semaphores}
\label{ch:semaphore}
\index{semaphore}
\glsadd{semaphore}

@@

\chapter{Bounded Buffer}
\label{ch:bb}
\index{bounded buffer}
\index{producer/consumer problem}
\glsadd{producer/consumer problem}

@@

\chapter{Split Binary Semaphores}
\label{ch:sbs}
\index{split binary semaphore}

@@

\chapter{Mesa Condition Variables in CXL}
\label{ch:mesa}

@@

\chapter{Actors and Synchronized Queues}
\label{ch:actor}
\index{actor model}
\glsadd{actor model}

@@

\chapter{Non-Blocking Synchronization}
\label{ch:nonblocking}
\index{non-blocking synchronization}
\glsadd{non-blocking synchronization}

@@

\chapter{Barrier Synchronization}
\label{ch:barrier}
\index{barrier synchronization}
\glsadd{barrier synchronization}

@@

\chapter{Networking: Alternating Bit Protocol}
\label{ch:abp}
\index{alternating bit protocol}
